Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-26 main-sketch.tex
fix sentences marked by Bun

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}%Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
\subtitle{Extended Abstract}
\begin{abstract}
Bayesian inference is a statistical method which allows one to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  Settings where sensitive individual information is , different approaches have been taken to make
this process differentially private. \citet{dimitrakakis2014robust},
and \citet{wang2015privacy}, for instance, proved that, under specific
conditions, sampling from the posterior distribution is already
differentially private. Other works,
e.g., \cite{zhang2016differential}, \cite{foulds2016theory}, designed
differentially private mechanisms that output a representation of the
full posterior distribution. Also, accuracy of these mechanisms was
measured using metrics on the space of the numeric parameters of the
posterior distribution, e.g., the $\ell_1$-norm.

@@

% \input{main-sketch} % TODO: replace with your brilliant paper!
% \input{macros}
\section{An informal motivation}
\label{sec_intro}
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about individuals on the dataset.
So, we need to noise the posterior belief in order to
protect the data set before releasing it. The question of how much noise to add
is usually answered with an $\epsilon$, and a sensitivity value.
Sensitivity can be computed in many different ways based on which metric space
is imposed on the output set of the mechanism, and yet in literature (\cite{zhang2016differential,xiao2012bayesian} )
only metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
Another approach, which we will explore here, is to impose a metric over probability measures.
An orthogonal question is that of how to measure the accuracy. Again,
that can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances over probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability measures can outperform
in term of accuracy approaches based on metric over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.
\section{Bayesian Inference Background}
\label{sec_background}
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
\[
  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of $\theta$ when
$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$. That is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distributions. In this case we say that the prior
is conjugate of the likelihood function. Using conjugate priors simplify calculcations and allows
for inference to be performed in a recursive fashion over the data.
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias}--
of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
the the vector of parameters of a categorical distributed random variable.
In the former case the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs=\langle x_1,\dots x_n \rangle, x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbf{R^{+}})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generealised beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where in $\iverson{\cdot}$ we use
Iverson bracket notation. Denoting by $\Delta\valpha$ the vector $\langle  \Delta\alpha_1,\dots \Delta\alpha_k \rangle$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the component wise  sum of vectors of reals.

\section{The Problem and Baseline approach}
\label{sec:base}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
%with truncating method come from algorithm designed by \citet{zhang2016differential}
where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, an upper bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
The choice of Hellinger distance was dictated by two facts, first of all it simplifies
calculations in the case of the probabilistic models considered here
and second of all it also provides straightforwardly bounds for
the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
% \section{Technical Problem Statement}
% \label{sec_bayesInfer}
% The posterior belief about parameters $\xis$ is inferred from the
% group of sensitive data. Because it is usually published in form of a
% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
% can relieve a lot of information about sensitive data. So, the
% sensitive information we want to protect here is the posterior belief,
% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
% it\cite{foulds2016theory}. Then it will be better if we can use a
% distance over two distributions to measure the accuracy than a
% distance over just parameters or values when we are protecting a
% distribution, for instance, Hellinger distance in our paper. When we
% measure the accuracy between true posterior and protected posterior
% using Hellinger distance, it would be better we can have a protection
% mechanism based on Hellinger distance. However, current mechanisms are
% mainly based on $l_1$ norm by Laplace mechanism
% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
% design our exponential mechanism over Hellinger distance to protect
% the whole posterior distribution.

@@

\[
  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]
where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference
process will produce an element from $\betaset$ that we denote by
$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
prior,  which from now on we consider fixed and we denote it by $\bprior$.

We can now define the mechanism $\hexpmech$ which,
given in input a sequence of observations $\dataobs$, $\epsilon>0$ and $\delta>0$,
produces an element $r$ in $\betaset$ with probability:

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t. to the global sensitivity of the scoring function but w.r.t. to the smooth sensitivity $S(\dataobs)$
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
\end{equation}
 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t. $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}
In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 0.8$, and $\delta = 0.00000001$.

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

@@

\paragraph{Increasing dimensions and data size with balanced dataset}
\label{subsubsec_vs_dimension}
In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
different sizes and different dimensions. The plot shows that increasing the number of dimensions have
a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
mechanism. Fixing the number of dimensions and increasing the data size shows that
the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
mechanism.
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
\label{fig_vs_dimension}
\end{figure}

\paragraph{Fixed data size and unbalaced datasets}
\label{subsubsec_vs_variance}
In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
of balance of the datasets. We  study this variable only under
two-dimensions $\betad$ distribution in order to be more concise. The plot shows
that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.

@@

These results although very motivating, are still not enough for real world applications.
Hence, we will continue our work in the follwoing directions:
\begin{enumerate}
  \item For now, we just have a intuitive idea on the accuracy
    behavior of our mechanisms, and not a precise formula or bound on it.
    When do our mechanisms perform better than the baseline mechanism and when they don't?
    How much influence will elements in Section \ref{sec_experiment} have on the
    accuracy? Are there any other important factors we missed? These are
    all questions w.r.t. the accuracy that we are going to explore next, and in a more
    principled and formal way.
\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
  Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
  This means that we could improve accuracy, by adding less noise --
  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
  it is worth exploring other distances over distributions. An interesting class
  of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
\end{enumerate}

>>>>

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}%Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
\subtitle{Extended Abstract}

\author{Gian Pietro Farina}
\affiliation{%
  \institution{University at Buffalo, SUNY}
}
\email{gianpiet@buffalo.edu}

\author{Jiawen Liu}
\affiliation{%
  \institution{University at Buffalo, SUNY}
}
\email{jliu223@buffalo.edu}

\author{Marco Gaboardi}
\affiliation{%
  \institution{University at Buffalo, SUNY}
}
\email{gaboardi@buffalo.edu}

\author{Mark Bun}
\affiliation{%
  \institution{Princeton University}
}
\email{mbun@cs.princeton.edu}

\begin{abstract}
Bayesian inference is a statistical method which allows one to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  Settings where sensitive individual information is , different approaches have been taken to make
this process differentially private. \citet{dimitrakakis2014robust},
and \citet{wang2015privacy}, for instance, proved that, under specific
conditions, sampling from the posterior distribution is already
differentially private. Other works,
e.g., \cite{zhang2016differential}, \cite{foulds2016theory}, designed
differentially private mechanisms that output a representation of the
full posterior distribution. Also, accuracy of these mechanisms was
measured using metrics on the space of the numeric parameters of the
posterior distribution, e.g., the $\ell_1$-norm.

@@

% \input{main-sketch} % TODO: replace with your brilliant paper!
% \input{macros}
\section{An informal motivation}
\label{sec_intro}
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about individuals on the dataset.
Differential privacy enables release of an approximate posterios distribution through the introduction of random noise. The amount of the noise that must be introduced depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to small changes in the data set.%So, we need to noise the posterior belief in order to protect the data set before releasing it. The question of how much noise to add is usually answered with an $\epsilon$, and a sensitivity value.
Sensitivity can be computed in many different ways based on which metric space
is imposed on the output set of the mechanism. In the literature on private Bayesian inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with respect to the vector of numbers parameterizing the output distribution using e.g. The $\ell_1$ norm.
%metrics over the numeric parameters, e.g. $\ell_1$ norm, are used.
%Another approach, which we will explore here, is to impose a metric over probability measures.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.

\section{Bayesian Inference Background}
\label{sec_background}
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
\[
  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression  $\Pr(\dataobs | \theta)$ denotes the \emph{likelihood} of observing $\dataobs$ under a value of $\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distributions. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior simplifies calculcations and allows for inference to be performed in a recursive fashion over the data.
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias}--
of a Bernoulli distributed random variable, and its immediate generalization where the parameter $\vtheta$ represents
the vector of parameters of a conjugate distributed random variable.
In the former case, the prior distribution over $\theta\in [0,1]$ is going to be a beta distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$represents Iverson bracket notation. Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the component wise sum of vectors of reals.

\section{The Problem and Baseline approach}
\label{sec:base}
We are interested in designing a mechanism for privately releasing the full posterior distributions derived in section \ref{sec_background}, as opposed to just sampling from them.  It's worth noticing that the posterior distributions are fully characterized by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the Beta-Binomial model we are interested in releasing a private version of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have already attacked this problem by adding independent Laplacian noise to the parameters of the posteriors. That is, in the case of the Beta-Binomial system, the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha + \tilde{\Delta \alpha},\beta + n - \tilde{\Delta \alpha})$ where $\tilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
calculations in the case of the probabilistic models considered here
and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
% \section{Technical Problem Statement}
% \label{sec_bayesInfer}
% The posterior belief about parameters $\xis$ is inferred from the
% group of sensitive data. Because it is usually published in form of a
% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
% can relieve a lot of information about sensitive data. So, the
% sensitive information we want to protect here is the posterior belief,
% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
% it\cite{foulds2016theory}. Then it will be better if we can use a
% distance over two distributions to measure the accuracy than a
% distance over just parameters or values when we are protecting a
% distribution, for instance, Hellinger distance in our paper. When we
% measure the accuracy between true posterior and protected posterior
% using Hellinger distance, it would be better we can have a protection
% mechanism based on Hellinger distance. However, current mechanisms are
% mainly based on $l_1$ norm by Laplace mechanism
% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
% design our exponential mechanism over Hellinger distance to protect
% the whole posterior distribution.

@@

\[
  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]

where $\Delta\alpha$ is as defined in Section \ref{sec_background}. Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference process will produce an element from $\betaset$ that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the prior,  which from now on we consider fixed and we denote it by $\bprior$.

We can now define the mechanism $\hexpmech$ which, given in input a sequence of observations $\dataobs$ and parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}

This mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as the range and $\hellinger(\cdot,\cdot)$ as the scoring function. The difference is that in this mechanism we don't calibrate the noise w.r.t. to the global sensitivity of the scoring function but w.r.t. to the smooth sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$, the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}
In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 0.8$, and $\delta = 10^{-8}$.

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned independent variables --or a combination thereof. The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median is also drawn to give a rough guide to the significance of difference of medians; The whiskers extend from the box to show the range of the data. A blue box in the plots represents our newly designed exponential mechanism behavior, while the yellow box next to it represents the performance of a variation of the basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior. The variation considered performs a post processing on the released parameters so that they are consistent. For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.

\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

@@

\paragraph{Increasing dimensions and data size with balanced dataset}
\label{subsubsec_vs_dimension}
In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of different sizes and different dimensions. The plot shows that increasing the number of dimensions has a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number of dimensions and increasing the data size shows that the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In other words, dimensions have little influence on whether our mechanisms will beat the Laplace mechanism.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
\label{fig_vs_dimension}
\end{figure}

\paragraph{Fixed data size and unbalaced datasets}
\label{subsubsec_vs_variance}
In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels of balance of the datasets. We  study this variable only under the two-dimensional $\betad$ distribution in order to be more concise. The plot shows that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.

@@

These results although very motivating, are still not enough for real world applications. Hence, we will continue our work in the follwoing directions:
\begin{enumerate}
  \item  For now, we just have a intuitive idea on the accuracy behavior of our mechanisms, and not a precise formula or bound on it. When do our mechanisms perform better than the baseline mechanism and when they don't? How much influence will elements in Section \ref{sec_experiment} have on the accuracy? Are there any other important factors we missed? These are all questions w.r.t. the accuracy that we are going to explore next, and in a more principled and formal way.
\item  Theorem \ref{thm:privacy} provides an upper bound on the  privacy loss for
  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one. Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$. This means that we could improve accuracy, by adding less noise -- that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
\item The choice of the Hellinger distance might seem quite ad-hoc. Hence, it is worth exploring other distances over distributions. An interesting class of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
\end{enumerate}
